---
title: "QGIS Drive link"
output: html_notebook
---

in the following scenario:

- geotagged pictures present on local computer
- same pictures also uploaded to google drive
- import geotagged pictures in QGIS

with the aim to:

- create a qgis2web map that automatically has the link to the pictures

This scripts does the magic, by finding the google drive link of the images and adding it to the shapefile

For details on teh QGIS side see https://opengislab.com/blog/2020/8/23/mapping-and-viewing-geotagged-photos-in-qgis 

```{r}
library(tidyverse)
library(googledrive)
library(sf)
library(progressr)
library(fs)
handlers("progress")
```

```{r}
# List of folders where the pictures are in
# doesn't support nested folders
drive_folders <- list(
  'https://drive.google.com/drive/u/3/folders/1X1W3CVnSxvTgw5dS3QIst-r1qsovCKv4',
  'https://drive.google.com/drive/u/3/folders/1vWHIDwTZmmDmOMCBtH1E5wGXsZx0gAIR',
  'https://drive.google.com/drive/u/3/folders/1mOMOrgI1blZ-cKfhUMDIroXkh0tJweCb'
  )

# shapefile obtained by using the QGIS tool `import geotagged pictures`
picture_shapefile <- "/home/simone/Documents/uni/botanical excursion/layer_geotagged_pictures.gpkg"
# The html template used in the picture, probably no need the change it
html_template <- "<img src='{img_url}' width=100% >"
```

```{r}
folder_query <- drive_folders %>% 
  map_chr(as_id) %>% 
  map_chr(~str_glue("'{.x}' in parents")) %>% 
  paste(collapse = " or ")
```




```{r}
get_image_url <- function(img_name) {
  img <-
    drive_find(
      type = drive_mime_type("jpeg"),
      q = folder_query,
      q = str_glue("name contains '{img_name}'")
    )
  
  if (nrow(img) == 0) {
    rlang::inform(str_glue("{img_name} not found on google drive"))
    ""
  }
  else{
    if (nrow(img) > 1) {
      rlang::inform(str_glue("{img_name} matches multiple images. Returning first"))
    }
    img$drive_resource[[1]]$webContentLink
  }
  
}

get_images_url <- function(img_names){
  p <- progressor(along = img_names)
  img_names %>%
    map_chr(\(img_name) {
      p(message = img_name)
      get_image_url(img_name)
    })  
}

get_images_html <- function(imgs_url) {
  imgs_url %>%
    map_chr(\(img_url) {
      ifelse(img_url == "", "", str_glue(html_template))
    })
}
```


```{r}
pictures_html <- pictures_layer %>% 
  mutate(url = get_images_url(filename), html = get_images_html(url)  )
```

```{r}
pictures_html
```



```{r}
st_write(pictures_html, paste0(path_ext_remove(picture_shapefile), "_html.", path_ext(picture_shapefile)), append=FALSE)
```

